Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-06-30 conclusions.tex
Moved URL footnote for LIGO Data Grid to its first mention in the Results section
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1242 ccdd05d5-56c1-461a-bf98-85f6876523b4
Deleted commented-out text in conclusion
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1243 ccdd05d5-56c1-461a-bf98-85f6876523b4

The \lloid{} method is as fast as standard \fft{} convolutions but allows for
nearly latency-free, real-time operation.  We anticipate requiring $\sim$100
modern multi-core computers to search for binary neutron stars using
coincident \GW\ data from a multi-detector network.  In the future, additional
computational savings could be acheived by conditionally reconstructing the
\SNR{} time-series only during times when a composite detection statistic
crosses a threshold~\citep{svd-compdetstat}.  However, the anticipated required
number of computers is well within the current computing capabilities of the
\LIGO{} Data
Grid\footnote{\url{https://www.lsc-group.phys.uwm.edu/lscdatagrid/}}.

@@

\begin{comment}
The detection algorithm we described has no intrinsic latency.  However, there
are fundamental and practical latencies associated with the analysis and
detection procedure. For example, the \LIGO{} data acquisition records science
data in 1/16~s blocks~\citep{Bork2001}. Data must also be aggregated from all
of the \GW\ observatories using global computer networks capable of high
bandwidth but perhaps only modest latency.  This could introduce a latency of
$\sim$100~ms.  Lastly, the software implementation of the algorithm itself may
introduce latency.  
\end{comment}

@@

\begin{comment}
Another potential complication is that if adjacent time slices have non-negligible
cross-correlation with each other, then there may be some subtleties in the design
of the triggering and coincidence stages that we must address in order to translate
the early-warning outputs into candidate events.  On the other hand, the time-slice
decomposition and the \SVD\ may be beneficial for the postprocessing stage
because they will help us form low-latency signal-based vetoes (e.g. $\chi^2$ statistics)
that have been essential for glitch rejection used in previous \GW{} \CBC{}
searches.
\end{comment}

@@

%Latency budget, including `before' and `after' quotes for:

%\begin{itemize}
%\item Data acquisition
%\item Calibration
%\item Data aggregation
%\item Analysis
%\item Localization
%\item Alert
%\item Telescope actuation
%\item Total
%\end{itemize}

>>>>

The \lloid{} method is as fast as standard \fft{} convolutions but allows for
nearly latency-free, real-time operation.  We anticipate requiring $\sim$100
modern multi-core computers to search for binary neutron stars using
coincident \GW\ data from a multi-detector network.  In the future, additional
computational savings could be acheived by conditionally reconstructing the
\SNR{} time-series only during times when a composite detection statistic
crosses a threshold~\citep{svd-compdetstat}.  However, the anticipated required
number of computers is well within the current computing capabilities of the
\LIGO{} Data Grid.

@@

@@

@@
